Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 introduction.tex
addressing more reviewer comments.

We demonstrate how Titan is more efficient utilized by the mixing of small and
short-lived tasks in backfill with regular payloads. Cycles otherwise unusable
(or very difficult to use) are used for science thus, increasing the overall
utilization on Titan without loss of quality-of-service. The conventional mix
of jobs at OLCF cannot be effectively backfilled because of size, duration,
and scheduling policies. Our approach is extensible to any HPC with
"capability scheduling" policies.  We also investigate a pilot-abstraction
based task execution runtime system which allows advanced execution modes of
the ATLAS workload, as well as heterogeneous workloads, e.g., molecular
dynamics. As such, our work is an exemplary use case for general approaches to
HPC and HTC integration.

This work demonstrates a viable production route to delivering large amounts
of computing resources to ATLAS and, in the future, to other experimental and
observational use cases.  This broadens the use of leadership computing while
demonstrating how distributed workflows can be integrated with leadership
resources, and thus how HTC and HPC workloads can be effectively accommodated
simultaneously.

>>>>

We demonstrate how Titan is more efficiently utilized by the mixing of small
and short-lived tasks in backfill with regular payloads. Cycles otherwise
unusable (or very difficult to use) are used for science thus, increasing the
overall utilization on Titan without loss of quality-of-service. The
conventional mix of jobs at OLCF cannot be effectively backfilled because of
size, duration, and scheduling policies. Our approach is extensible to any HPC
with "capability scheduling" policies.  We also investigate the use of a
pilot-abstraction based task execution runtime system to flexibly execute
ATLAS and other heterogeneous workloads (molecular dynamics) using regular
queues. As such, our approach provides a general solution and investigation of
the convergence of HPC and HTC execution of workloads.

This work demonstrates a viable production route to delivering large amounts
of computing resources to ATLAS and, in the future, to other experimental and
observational use cases.  This broadens the use of leadership computing while
demonstrating how distributed workflows can be integrated with leadership
resources, and effectively accommodating HTC and HPC workloads simultaneously.
